Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
more updates
another update - S4.1

\noindent
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug.

@@

Our approach was capable of slicing a total of $260$ faults from $5$ different 
sujects. We are still running experiments for the \closure{} and \cmath{} projects.
(The results of these faults will be integrated on the camera-ready if accepted).
$33$ of the $260$ faults do not include the faulty statements in the slicer report
after slicing.

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes of the projects. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using

>>>>

\noindent
where $C$ is the cost of diagnosis. $C$ is the mean ranking of all buggy statements.
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost of
locating the bug. We also assume a perfect bug understanding, i.e., if the developer
sees the bug in the ranking, he can say it is the faulty one.

@@

Our approach was capable of slicing a total of $260$ faults from $5$ different 
subjects. We are still running experiments for the \closure{} and \cmath{} projects.
(The results of these faults will be integrated on the camera-ready if accepted).
$33$ of the $260$ faults do not include the faulty statements in the slicer report
after slicing.

@@

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. We only search
for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes of the projects. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements.
